Empirical Evaluation of eval in R

### 2020-08-27 inst/analysis/analysis_stable.Rmd

source("inc/paths.R")
source("inc/latextags.R")
source("inc/setup.R")
theme_set(theme_minimal())
create_tags(path(TAGS_DIR, "analysisStable.tex"), prefix="", default=TRUE)

@@

ast_sizes %>%
  ggplot(aes(x = dataset, y = expr_resolved_nodes, fill = dataset, weight = nb_ev_calls)) +
  geom_violin(trim = FALSE, width=.5)+
  geom_boxplot(width=.05) +
  scale_y_log10(labels = scales::comma) +
  labs(y="AST size (log)") +
  theme(
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

@@

```{r environment_hierarchy}
# classified_envir <- eval_calls %>% filter(!is.na(envir_expression)) %>%
#       mutate(env_class = pmap(list(environment_class, envir_type, envir_expression), extract_envir)) %>%
#       unnest_wider(env_class)

#TODO
```

>>>>

source("inc/paths.R")
source("inc/latextags.R")
source("inc/setup.R")
theme_set(theme_minimal())
theme_update(text = element_text(rel(1.5)))

create_tags(path(TAGS_DIR, "analysisStable.tex"), prefix="", default=TRUE)

@@

ast_sizes %>%
  ggplot(aes(x = dataset, y = expr_resolved_nodes, fill = dataset, weight = nb_ev_calls)) +
  geom_violin(trim = FALSE, width=.5)+
  geom_boxplot(width=.05) +
  scale_y_log10(labels = scales::comma) +
  labs(y="AST size (log)") +
  theme(
    #text=element_text(rel=2),
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

@@

```{r environment_hierarchy}
classified_envir <- eval_calls %>% filter(!is.na(envir_expression)) %>%
      mutate(env_class = pmap(list(environment_class, envir_type, envir_expression), extract_envir)) %>%
      hoist(env_class, read_env = 1, write_env = 2, .remove=FALSE) #Quicker when not removing

```{r write_env}

classified_envir %>% ggplot() +
  geom_bar(aes(x = write_env, weight = nb_ev_calls, group = dataset)) +
  labs(x = "Environment write")
```

```{r read_env}

classified_envir %>% ggplot() +
  geom_bar(aes(x = read_env, weight = nb_ev_calls, group = dataset)) +
  labs(x = "Environment reads")
```
